Trends of SDR in Thessaloniki

### 2023-06-11 Article.Rmd
Commit 2023-06-11 20:17

---
title:         "Trends of SDR in Thessaloniki"
# header-includes:
author:
  - name:         Natsis Athanasios
    email:        natsisphysicist@gmail.com
    affiliation:  Laboratory of Atmospheric Physics
#    footnote:     1
    correspondingauthor: true
  - name:         Alkiviadis Bais
    email:        abais@auth.gr 
    affiliation:  Laboratory of Atmospheric Physics
    correspondingauthor: false
address:
  - code:         Laboratory of Atmospheric Physics
    organization: Aristotle University of Thessaloniki
    addressline:  Campus Box 149
    city:         Thessaloniki
    # state:        State
    postcode:     54124
    country:      Greece
#  - code:         Another University
#    organization: Department
#    addressline:  A street 29
#    postcode:     2054 NX
#    city:         Manchester,
#    country:      The Netherlands
# footnote:
#   - code:         1
#     text:         "This is the first author footnote."
#   - code:         2
#     text:         "Another author footnote."
abstract: |
  Study of GHI and DNI radiation for 'clear-sky' and all-sky conditions.
  It consists of two paragraphs.
keywords: 
  - GHI
  - SDR
  - Solar Brigthening/Dimming
journal:        "An awesome journal"
date:           "`r Sys.Date()`"
classoption:    preprint, 3p, authoryear
bibliography:   references.bib
linenumbers:    false
numbersections: true
output: 
  bookdown::pdf_document2:
    number_sections:  no
    fig_caption:      yes
    keep_tex:         yes
    latex_engine:     xelatex
    toc:              yes
    toc_depth:        4
    fig_width:        7
    fig_height:       4.5
    documentclass:    article
    classoption:      a4paper,oneside
    fontsize:         12pt
    geometry:         "left=0.75in,right=0.75in,top=0.75in,bottom=0.75in"
    link-citations:   yes
    colorlinks:       yes
    urlcolor:         blue
    biblio-style:     apalike
  rticles::elsevier_article:
    keep_tex:         false
    citation_package: natbib
# date:           "`r format(Sys.time(), '%F')`"
---

@@

>>>>

---
title:         "Trends of SDR in Thessaloniki"
# header-includes:
author:
  - name:         Natsis Athanasios
    email:        natsisphysicist@gmail.com
    affiliation:  Laboratory of Atmospheric Physics
#    footnote:     1
    correspondingauthor: true
  - name:         Alkiviadis Bais
    email:        abais@auth.gr 
    affiliation:  Laboratory of Atmospheric Physics
    correspondingauthor: false
address:
  - code:         Laboratory of Atmospheric Physics
    organization: Aristotle University of Thessaloniki
    addressline:  Campus Box 149
    city:         Thessaloniki
    # state:        State
    postcode:     54124
    country:      Greece
#  - code:         Another University
#    organization: Department
#    addressline:  A street 29
#    postcode:     2054 NX
#    city:         Manchester,
#    country:      The Netherlands
# footnote:
#   - code:         1
#     text:         "This is the first author footnote."
#   - code:         2
#     text:         "Another author footnote."
abstract: |
  Study of GHI and DNI radiation for 'clear-sky' and all-sky conditions.
  It consists of two paragraphs.
keywords: 
  - GHI
  - SDR
  - Solar Brigthening/Dimming
journal:        "An awesome journal"
date:           "`r Sys.Date()`"
classoption:    preprint, 3p, authoryear
bibliography:   references.bib
linenumbers:    false
numbersections: true
output: 
  rticles::elsevier_article:
    keep_tex:         false
    citation_package: natbib
  bookdown::pdf_document2:
    number_sections:  no
    fig_caption:      yes
    keep_tex:         yes
    latex_engine:     xelatex
    toc:              yes
    toc_depth:        4
    fig_width:        7
    fig_height:       4.5
    documentclass:    article
    classoption:      a4paper,oneside
    fontsize:         12pt
    geometry:         "left=0.75in,right=0.75in,top=0.75in,bottom=0.75in"
    link-citations:   yes
    colorlinks:       yes
    urlcolor:         blue
    biblio-style:     apalike
# date:           "`r format(Sys.time(), '%F')`"
---

@@

```{r , echo=F, fig.cap="Trendns."}
knitr::include_graphics("./images/SzaTrends-5.pdf")
```

```{r , echo=F, fig.cap="Trendns."}
knitr::include_graphics("./images/SzaTrends-13.pdf")
```

```{r , echo=F, fig.cap="Trendns."}
knitr::include_graphics("./images/SzaTrends-21.pdf")
```

```{r, fig.cap='Figure 1', fig.subcap=c('(a)', '(b)', '(c)')}
plot(1:10)
plot(cars, pch = 19)
boxplot(Sepal.Width ~ Species, data = iris)
```
